Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
adding my comment.
add comment.
making paragraphs be the almost same size.
moving citation for Haddock to the first appearance.

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to reqire more details and drive the
implementation closer to the desired goal.  Rinse and repeat.  BDD
includes TDD, but with a terminology and mindset  shifted towards
specification instead of testing. BDD also includes other software
development methods, such as automatic test discovery and continuous
integration~\cite{ci}.  In BDD, specifications can be used for
automatic testing.

BDD-style TDD has been pioneered by RSpec~\cite{rspec}.  In this
paper, we explore how to apply the TDD aspect of BDD to Haskell.

@@

We made two observations:
\begin{enumerate}
    \item
        Parts of a specification can be useful as user documentation.
    \item
        Doctest, a tool inspired by a Python module with the same
        name~\cite{doctest}, already allows to verify
        \emph{interactive examples} in Haddock comments.
\end{enumerate}

@@

\begin{quote}
    \emph{sol: Can we remove what follows??}
\end{quote}

@@

@@

The standard documentation mechanism for Haskell is
Haddock~\cite{haddock}.
Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.

>>>>

In other programming language communities, behavior driven development
(BDD) is getting much attention, and is slowly replacing test driven
development (TDD).  TDD is an iterative style of software development
where the developer first writes a few test cases, then implements the
software in the simplest possible way which makes the test cases pass.
That could mean yielding a constant value at first.  Subsequently,
more test cases are written to reqire more details and drive the
implementation closer to the desired goal.  Rinse and repeat.

BDD includes TDD, but with a terminology and mindset shifted towards
specification instead of testing. BDD also includes other software
development methods, such as automatic test discovery and continuous
integration~\cite{ci}.  In BDD, specifications can be used for
automatic testing.  BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

@@

We made two observations:
\begin{enumerate}
    \item
        Parts of a specification can be useful as user documentation.
    \item
        Doctest, a tool inspired by a Python module with the same
        name~\cite{doctest}, already allows to verify
        \emph{interactive examples} in Haddock~\cite{haddock} comments.
\end{enumerate}

@@

\begin{quote}
    \emph{sol: Can we remove what follows??}
    \emph{kazu: I want to keep them for readability??}
\end{quote}

@@

    kazu: ``behavior'' sounded strange at least to me at the first time.
    We alreay supported this word with typeclassopedia. So, I think
    this paragraph is completed.

@@

The standard documentation mechanism for Haskell is
Haddock.
Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.
